MRP Case Study

### 2020-02-14 Code/mrp/Case Study .Rmd
starting to look at creating a list as an input to the stan code
Modifications to hierarchal model with new sample data.

```{r echo=FALSE}

J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
        for (i4 in 1:J[4]){
          for (i5 in 1:J[5]){
              count <- count + 1
              # Fill them in so we know what category we are referring to
              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
          }
        }
      }
    }
  }
  # Proportion in each sample in the population
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.5, 0.2, 0.3)
  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
  p_income<-c(.50,.35,.15)
  p_state_tmp<-runif(50,10,20)
  p_state<-p_state_tmp/sum(p_state_tmp)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
  }

  # Now let's adjust for the probability of response
  p_response_baseline <- 0.01
  p_response_male <- c(2, 0.8) / 2.8
  p_response_eth <- c(1, 1.2, 2.5) / 4.7
  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
  p_response_inc <- c(1, 0.9, 0.8) / 2.7
  p_response_state <- rbeta(50, 1, 1)
  p_response_state <- p_response_state / sum(p_response_state)
  p_response <- rep(NA, prod(J))
  for (j in 1:prod(J)) {
    p_response[j] <-
      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
  }

  coef_male <- c(0,-0.3)
  coef_eth <- c(0, 0.6, 0.9)
  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
  coef_income <- c(0,-0.2, 0.6)
  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
  true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
  for (j in 1:prod(J)) {
    true_popn$satisfaction[j] <- plogis(
      coef_male[poststrat[j, 1] + 1] +
        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
      )
  }
```

@@

  real satisfaction[N];                        // Vector of observations.
  int<lower = 1, upper = K> male[N];        // Vector of group assignments.
  int eth[N];                               // Vector of ethnicity covariates.
  int age[N];                               // Vector of age covariates.
  int income[N];                          // Vector of income covariates.
  int state[N];                          // Vector of state covariates.

@@

// Parameters and hyperparameters.
parameters {
  matrix[K, (I - 1)] alpha;              // Matrix of observation-level brand coefficients.
  vector[K] beta;                        // Vector of observation-level price coefficients.
  real gamma;                            // Mean of the population model.
  real<lower=0> tau;                     // Variance of the population model.
  real<lower=0> sigma;                   // Variance of the observation model.
}

@@

  // Population model and likelihood.
  for (k in 1:K) {
    alpha[k,] ~ normal(gamma, tau);
    beta[k] ~ normal(gamma, tau);
  }
  for (n in 1:N) {
    mu[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
    income[n] + beta[male[n]] * state[n];
  }
  cat_pref ~ normal(mu, sigma);
}

// Generate predictions using the posterior.
generated quantities {
  vector[N] mu_pc;                       // Declare mu for predicted linear model.
  real cat_pref_pc[N];                     // Vector of predicted observations.

  // Generate posterior prediction distribution.
  for (n in 1:N) {
    mu_pc[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
    income[n] + beta[male[n]] * state[n];
    cat_pref_pc[n] = normal_rng(mu_pc[n], sigma);
  }
}

>>>>

```{r}
mrp_sim <- simulate_mrp_data(n=1200)
sample <- mrp_sim[["sample"]]

print(sample)
```

```{r echo=FALSE}
# 
# J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
#   poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
#   colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
#   count <- 0
#   for (i1 in 1:J[1]){
#     for (i2 in 1:J[2]){
#       for (i3 in 1:J[3]){
#         for (i4 in 1:J[4]){
#           for (i5 in 1:J[5]){
#               count <- count + 1
#               # Fill them in so we know what category we are referring to
#               poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
#           }
#         }
#       }
#     }
#   }
#   # Proportion in each sample in the population
#   p_male <- c(0.52, 0.48)
#   p_eth <- c(0.5, 0.2, 0.3)
#   p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
#   p_income<-c(.50,.35,.15)
#   p_state_tmp<-runif(50,10,20)
#   p_state<-p_state_tmp/sum(p_state_tmp)
#   poststrat$N<-0
#   for (j in 1:prod(J)){
#     poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
#       p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
#   }
# 
#   # Now let's adjust for the probability of response
#   p_response_baseline <- 0.01
#   p_response_male <- c(2, 0.8) / 2.8
#   p_response_eth <- c(1, 1.2, 2.5) / 4.7
#   p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
#   p_response_inc <- c(1, 0.9, 0.8) / 2.7
#   p_response_state <- rbeta(50, 1, 1)
#   p_response_state <- p_response_state / sum(p_response_state)
#   p_response <- rep(NA, prod(J))
#   for (j in 1:prod(J)) {
#     p_response[j] <-
#       p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
#       p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
#       p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
#   }
# 
#   coef_male <- c(0,-0.3)
#   coef_eth <- c(0, 0.6, 0.9)
#   coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
#   coef_income <- c(0,-0.2, 0.6)
#   coef_state <- c(0, round(rnorm(49, 0, 1), 1))
#   coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
#                            c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
#   true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
#   for (j in 1:prod(J)) {
#     true_popn$satisfaction[j] <- plogis(
#       coef_male[poststrat[j, 1] + 1] +
#         coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
#         coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
#         coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
#       )
#   }
```

@@

  real service_failure[N];                        // Vector of observations.
  int<lower = 1, upper = K> male[N];        // Vector of group assignments.
  int age[N];                               // Vector of ethnicity covariates.
  int eth[N];                               // Vector of age covariates.
  int income[N];                          // Vector of income covariates.
  int state[N];                          // Vector of state covariates.

@@

// Parameters and hyperparameters.
parameters {
  matrix[K, (I - 1)] alpha;              // Matrix of observation-level gender coefficients.
  vector[K] beta;                        // Vector of all other observation-level coefficients.
  real gamma;                            // Mean of the population model.
  real<lower=0> tau;                     // Variance of the population model.
  real<lower=0> sigma;                   // Variance of the observation model.
}

@@

  // Population model and likelihood.
  for (k in 1:K) {
    alpha[k,] ~ normal(gamma, tau);
    beta[k] ~ normal(gamma, tau);
  }
  for (n in 1:N) {
    mu[n] = alpha[male[n], age[n]] + beta[male[n]] * eth[n] + beta[male[n]] * 
    income[n] + beta[male[n]] * state[n];
  }
  service_failure ~ normal(mu, sigma);
}

// Generate predictions using the posterior.
generated quantities {
  vector[N] mu_pc;                       // Declare mu for predicted linear model.
  real service_failure_pc[N];                     // Vector of predicted observations.

  // Generate posterior prediction distribution.
  for (n in 1:N) {
    mu_pc[n] = alpha[male[n], age[n]] + beta[male[n]] * eth[n] + beta[male[n]] * 
    income[n] + beta[male[n]] * state[n];
    service_failure_pc[n] = normal_rng(mu_pc[n], sigma);
  }
}
